### 2025-02-24 paper/preprint/paper.tex
added Aleks as author to preprint

\usepackage{arxiv}
\usepackage{orcidlink}
\usepackage{amsmath}
\usepackage[T1]{fontenc}
\usepackage{placeins}
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[skins,breakable]{tcolorbox}}
\@ifpackageloaded{fontawesome5}{}{\usepackage{fontawesome5}}
\definecolor{quarto-callout-color}{HTML}{909090}
\definecolor{quarto-callout-note-color}{HTML}{0758E5}
\definecolor{quarto-callout-important-color}{HTML}{CC1914}
\definecolor{quarto-callout-warning-color}{HTML}{EB9113}
\definecolor{quarto-callout-tip-color}{HTML}{00A047}
\definecolor{quarto-callout-caution-color}{HTML}{FC5300}
\definecolor{quarto-callout-color-frame}{HTML}{acacac}
\definecolor{quarto-callout-note-color-frame}{HTML}{4582ec}
\definecolor{quarto-callout-important-color-frame}{HTML}{d9534f}
\definecolor{quarto-callout-warning-color-frame}{HTML}{f0ad4e}
\definecolor{quarto-callout-tip-color-frame}{HTML}{02b875}
\definecolor{quarto-callout-caution-color-frame}{HTML}{fd7e14}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\usepackage{amsthm}
\theoremstyle{definition}
\newtheorem{example}{Example}[section]
\theoremstyle{definition}
\newtheorem{exercise}{Parameters}[section]
\theoremstyle{plain}
\newtheorem{proposition}{Proposition}[section]
\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]
\theoremstyle{plain}
\newtheorem{corollary}{Research Question}[section]
\theoremstyle{remark}
\AtBeginDocument{\renewcommand*{\proofname}{Proof}}
\newtheorem*{remark}{Remark}
\newtheorem*{solution}{Solution}
\newtheorem{refremark}{Remark}[section]
\newtheorem{refsolution}{Solution}[section]
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Limited to classification models.
\item
  Proxy attributes of immutable features.
\item
  Increased training time.
\end{enumerate}

@@

@@

@@

\begin{tcolorbox}[enhanced jigsaw, breakable, title=\textcolor{quarto-callout-warning-color}{\faExclamationTriangle}\hspace{0.5em}{Warning}, opacitybacktitle=0.6, titlerule=0mm, colback=white, opacityback=0, bottomrule=.15mm, colbacktitle=quarto-callout-warning-color!10!white, coltitle=black, arc=.35mm, toptitle=1mm, toprule=.15mm, bottomtitle=1mm, rightrule=.15mm, leftrule=.75mm, colframe=quarto-callout-warning-color-frame, left=2mm]

@@

@@

\begin{tcolorbox}[enhanced jigsaw, breakable, title=\textcolor{quarto-callout-note-color}{\faInfo}\hspace{0.5em}{Note}, opacitybacktitle=0.6, titlerule=0mm, colback=white, opacityback=0, bottomrule=.15mm, colbacktitle=quarto-callout-note-color!10!white, coltitle=black, arc=.35mm, toptitle=1mm, toprule=.15mm, bottomtitle=1mm, rightrule=.15mm, leftrule=.75mm, colframe=quarto-callout-note-color-frame, left=2mm]

@@

For the initial round of experiments we

@@

  \begin{itemize}
  \tightlist
  \item
    \(\lambda_{\text{cost}}\): \texttt{0.0,\ 0.001,\ 0.1}
  \item
    \(\lambda_{\text{div}}\):
    \texttt{0.01,\ 0.05,\ 0.1,\ 0.5,\ 1.0,\ 5.0,\ 10.0,\ 15.0}
  \item
    Learning Rate: \texttt{1.0}
  \item
    Maximum Iterations: \texttt{20,\ 50,\ 100}
  \item
    Optimizerimizer: \texttt{sgd}
  \end{itemize}
\item
  Generator: \texttt{ecco,\ generic,\ omni,\ revise}
\item
  Training Parameters:

@@

  \toprule
  \textbf{Objective} & \textbf{$\lambda_{\text{div}} (\text{train})$} & \textbf{Generator} & \textbf{Value} & \textbf{Std} \\\midrule
  \endfirsthead
  \toprule
  \textbf{Objective} & \textbf{$\lambda_{\text{div}} (\text{train})$} & \textbf{Generator} & \textbf{Value} & \textbf{Std} \\\midrule
  \endhead
  \bottomrule
  \multicolumn{5}{r}{Continuing table below.}\\
  \bottomrule
  \endfoot
  \endlastfoot
  full & 0.01 & \textit{ECCo} & $-9.91 \cdot 10^{11}$ & $2.25 \cdot 10^{12}$ \\
  full & 0.01 & \textit{Generic} & $-5.71 \cdot 10^{17}$ & $1.3 \cdot 10^{18}$ \\
  \color{blue}{\textbf{full}} & \color{blue}{\textbf{0.01}} & \color{blue}{\textbf{Omniscient}} & \color{blue}{\textbf{-2.54}} & \color{blue}{\textbf{0.116}} \\
  full & 0.01 & \textit{REVISE} & -15.6 & 13.2 \\
  vanilla & 0.01 & \textit{ECCo} & -4.28 & 3.52 \\
  vanilla & 0.01 & \textit{Generic} & -4.45 & 3.47 \\
  vanilla & 0.01 & \textit{Omniscient} & -5.12 & 4.46 \\
  vanilla & 0.01 & \textit{REVISE} & -4.91 & 4.24 \\
  full & 0.05 & \textit{ECCo} & $-5.63 \cdot 10^{5}$ & $1.28 \cdot 10^{6}$ \\
  full & 0.05 & \textit{Generic} & $-8.35 \cdot 10^{17}$ & $1.9 \cdot 10^{18}$ \\
  \color{blue}{\textbf{full}} & \color{blue}{\textbf{0.05}} & \color{blue}{\textbf{Omniscient}} & \color{blue}{\textbf{-2.53}} & \color{blue}{\textbf{0.114}} \\
  full & 0.05 & \textit{REVISE} & -15 & 12.6 \\
  vanilla & 0.05 & \textit{ECCo} & -4.4 & 3.66 \\
  vanilla & 0.05 & \textit{Generic} & -4.38 & 3.48 \\
  vanilla & 0.05 & \textit{Omniscient} & -5.25 & 4.62 \\
  vanilla & 0.05 & \textit{REVISE} & -4.94 & 4.22 \\
  full & 0.1 & \textit{ECCo} & $-6.74 \cdot 10^{5}$ & $1.53 \cdot 10^{6}$ \\
  full & 0.1 & \textit{Generic} & $-1.71 \cdot 10^{11}$ & $3.9 \cdot 10^{11}$ \\
  \color{blue}{\textbf{full}} & \color{blue}{\textbf{0.1}} & \color{blue}{\textbf{Omniscient}} & \color{blue}{\textbf{-2.56}} & \color{blue}{\textbf{0.124}} \\
  full & 0.1 & \textit{REVISE} & -15.6 & 13.2 \\
  vanilla & 0.1 & \textit{ECCo} & -4.28 & 3.52 \\
  vanilla & 0.1 & \textit{Generic} & -4.45 & 3.48 \\
  vanilla & 0.1 & \textit{Omniscient} & -5.12 & 4.46 \\
  vanilla & 0.1 & \textit{REVISE} & -4.91 & 4.25 \\
  full & 0.5 & \textit{ECCo} & -11.8 & 9.83 \\
  full & 0.5 & \textit{Generic} & $-1.06 \cdot 10^{18}$ & $2.42 \cdot 10^{18}$ \\
  \color{blue}{\textbf{full}} & \color{blue}{\textbf{0.5}} & \color{blue}{\textbf{Omniscient}} & \color{blue}{\textbf{-2.54}} & \color{blue}{\textbf{0.123}} \\
  full & 0.5 & \textit{REVISE} & -15 & 12.6 \\
  vanilla & 0.5 & \textit{ECCo} & -4.4 & 3.65 \\
  vanilla & 0.5 & \textit{Generic} & -4.38 & 3.48 \\
  vanilla & 0.5 & \textit{Omniscient} & -5.25 & 4.61 \\
  vanilla & 0.5 & \textit{REVISE} & -4.95 & 4.22 \\
  full & 1 & \textit{ECCo} & -11.5 & 11.1 \\
  full & 1 & \textit{Generic} & $-1.71 \cdot 10^{11}$ & $3.88 \cdot 10^{11}$ \\
  \color{blue}{\textbf{full}} & \color{blue}{\textbf{1}} & \color{blue}{\textbf{Omniscient}} & \color{blue}{\textbf{-2.59}} & \color{blue}{\textbf{0.117}} \\
  full & 1 & \textit{REVISE} & -15.7 & 13.3 \\
  vanilla & 1 & \textit{ECCo} & -4.28 & 3.51 \\
  vanilla & 1 & \textit{Generic} & -4.44 & 3.47 \\
  vanilla & 1 & \textit{Omniscient} & -5.11 & 4.46 \\
  vanilla & 1 & \textit{REVISE} & -4.91 & 4.25 \\
  full & 5 & \textit{ECCo} & -3.99 & 3.12 \\
  full & 5 & \textit{Generic} & $-4.88 \cdot 10^{17}$ & $1.11 \cdot 10^{18}$ \\
  \color{blue}{\textbf{full}} & \color{blue}{\textbf{5}} & \color{blue}{\textbf{Omniscient}} & \color{blue}{\textbf{-2.53}} & \color{blue}{\textbf{0.117}} \\
  full & 5 & \textit{REVISE} & -14.6 & 12.1 \\
  vanilla & 5 & \textit{ECCo} & -4.4 & 3.65 \\
  vanilla & 5 & \textit{Generic} & -4.38 & 3.48 \\
  vanilla & 5 & \textit{Omniscient} & -5.25 & 4.61 \\
  vanilla & 5 & \textit{REVISE} & -4.95 & 4.22 \\
  \color{blue}{\textbf{full}} & \color{blue}{\textbf{10}} & \color{blue}{\textbf{ECCo}} & \color{blue}{\textbf{-2.31}} & \color{blue}{\textbf{0.735}} \\
  full & 10 & \textit{Generic} & $-1.7 \cdot 10^{11}$ & $3.86 \cdot 10^{11}$ \\
  full & 10 & \textit{Omniscient} & -2.53 & 0.117 \\
  full & 10 & \textit{REVISE} & -15.5 & 13 \\
  vanilla & 10 & \textit{ECCo} & -4.28 & 3.51 \\
  vanilla & 10 & \textit{Generic} & -4.44 & 3.47 \\
  vanilla & 10 & \textit{Omniscient} & -5.12 & 4.46 \\
  vanilla & 10 & \textit{REVISE} & -4.91 & 4.24 \\
  \color{blue}{\textbf{full}} & \color{blue}{\textbf{15}} & \color{blue}{\textbf{ECCo}} & \color{blue}{\textbf{-2.01}} & \color{blue}{\textbf{0.488}} \\
  full & 15 & \textit{Generic} & $-4.91 \cdot 10^{17}$ & $1.12 \cdot 10^{18}$ \\
  full & 15 & \textit{Omniscient} & -2.53 & 0.116 \\
  full & 15 & \textit{REVISE} & -14.4 & 11.7 \\
  vanilla & 15 & \textit{ECCo} & -4.4 & 3.65 \\
  vanilla & 15 & \textit{Generic} & -4.38 & 3.48 \\
  vanilla & 15 & \textit{Omniscient} & -5.25 & 4.6 \\
  vanilla & 15 & \textit{REVISE} & -4.95 & 4.23 \\\bottomrule

@@

  \toprule
  \textbf{Objective} & \textbf{$\lambda_{\text{cost}} (\text{train})$} & \textbf{Generator} & \textbf{Value} & \textbf{Std} \\\midrule
  \endfirsthead
  \toprule
  \textbf{Objective} & \textbf{$\lambda_{\text{cost}} (\text{train})$} & \textbf{Generator} & \textbf{Value} & \textbf{Std} \\\midrule
  \endhead
  \bottomrule
  \multicolumn{5}{r}{Continuing table below.}\\
  \bottomrule
  \endfoot
  \endlastfoot
  full & 0 & \textit{ECCo} & $-5.32 \cdot 10^{3}$ & $1.21 \cdot 10^{4}$ \\
  full & 0 & \textit{Generic} & $-1.03 \cdot 10^{18}$ & $2.34 \cdot 10^{18}$ \\
  \color{blue}{\textbf{full}} & \color{blue}{\textbf{0}} & \color{blue}{\textbf{Omniscient}} & \color{blue}{\textbf{-2.64}} & \color{blue}{\textbf{0.125}} \\
  full & 0 & \textit{REVISE} & -15.4 & 12.9 \\
  vanilla & 0 & \textit{ECCo} & -4.34 & 3.58 \\
  vanilla & 0 & \textit{Generic} & -4.41 & 3.48 \\
  vanilla & 0 & \textit{Omniscient} & -5.18 & 4.54 \\
  vanilla & 0 & \textit{REVISE} & -4.93 & 4.23 \\
  full & 0.001 & \textit{ECCo} & -362 & 811 \\
  full & 0.001 & \textit{Generic} & $-2.65 \cdot 10^{17}$ & $6.04 \cdot 10^{17}$ \\
  \color{blue}{\textbf{full}} & \color{blue}{\textbf{0.001}} & \color{blue}{\textbf{Omniscient}} & \color{blue}{\textbf{-2.49}} & \color{blue}{\textbf{0.115}} \\
  full & 0.001 & \textit{REVISE} & -15.5 & 13 \\
  vanilla & 0.001 & \textit{ECCo} & -4.34 & 3.58 \\
  vanilla & 0.001 & \textit{Generic} & -4.41 & 3.48 \\
  vanilla & 0.001 & \textit{Omniscient} & -5.18 & 4.53 \\
  vanilla & 0.001 & \textit{REVISE} & -4.93 & 4.23 \\
  full & 0.1 & \textit{ECCo} & $-3.72 \cdot 10^{11}$ & $8.46 \cdot 10^{11}$ \\
  full & 0.1 & \textit{Generic} & $-4.48 \cdot 10^{14}$ & $1.02 \cdot 10^{15}$ \\
  \color{blue}{\textbf{full}} & \color{blue}{\textbf{0.1}} & \color{blue}{\textbf{Omniscient}} & \color{blue}{\textbf{-2.5}} & \color{blue}{\textbf{0.112}} \\
  full & 0.1 & \textit{REVISE} & -14.6 & 12.2 \\
  vanilla & 0.1 & \textit{ECCo} & -4.34 & 3.58 \\
  vanilla & 0.1 & \textit{Generic} & -4.41 & 3.48 \\
  vanilla & 0.1 & \textit{Omniscient} & -5.18 & 4.54 \\
  vanilla & 0.1 & \textit{REVISE} & -4.93 & 4.24 \\\bottomrule

@@

>>>>

\usepackage{arxiv}
\usepackage{orcidlink}
\usepackage{amsmath}
\usepackage[T1]{fontenc}
\usepackage{placeins}
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[skins,breakable]{tcolorbox}}
\@ifpackageloaded{fontawesome5}{}{\usepackage{fontawesome5}}
\definecolor{quarto-callout-color}{HTML}{909090}
\definecolor{quarto-callout-note-color}{HTML}{0758E5}
\definecolor{quarto-callout-important-color}{HTML}{CC1914}
\definecolor{quarto-callout-warning-color}{HTML}{EB9113}
\definecolor{quarto-callout-tip-color}{HTML}{00A047}
\definecolor{quarto-callout-caution-color}{HTML}{FC5300}
\definecolor{quarto-callout-color-frame}{HTML}{acacac}
\definecolor{quarto-callout-note-color-frame}{HTML}{4582ec}
\definecolor{quarto-callout-important-color-frame}{HTML}{d9534f}
\definecolor{quarto-callout-warning-color-frame}{HTML}{f0ad4e}
\definecolor{quarto-callout-tip-color-frame}{HTML}{02b875}
\definecolor{quarto-callout-caution-color-frame}{HTML}{fd7e14}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\usepackage{amsthm}
\theoremstyle{definition}
\newtheorem{exercise}{Parameters}[section]
\theoremstyle{definition}
\newtheorem{example}{Example}[section]
\theoremstyle{plain}
\newtheorem{corollary}{Research Question}[section]
\theoremstyle{plain}
\newtheorem{proposition}{Proposition}[section]
\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]
\theoremstyle{remark}
\AtBeginDocument{\renewcommand*{\proofname}{Proof}}
\newtheorem*{remark}{Remark}
\newtheorem*{solution}{Solution}
\newtheorem{refremark}{Remark}[section]
\newtheorem{refsolution}{Solution}[section]
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Limited to classification models.
\item
  Proxy attributes of immutable features.
\item
  Increased training time.
\item
  Training instabilities
\item
  Fairness and caveats (aware it's not a classical approach in this
  context, but there is a clear link).
\end{enumerate}

@@

\bibitem[\citeproctext]{ref-bezanson2017julia}
Bezanson, Jeff, Alan Edelman, Stefan Karpinski, and Viral B Shah. 2017.
{``Julia: A Fresh Approach to Numerical Computing.''} \emph{SIAM Review}
59 (1): 65--98. \url{https://doi.org/10.1137/141000671}.

\bibitem[\citeproctext]{ref-milan2023dataframes}
Bouchet-Valat, Milan, and Bogumił Kamiński. 2023. {``DataFrames.jl:
Flexible and Fast Tabular Data in Julia.''} \emph{Journal of Statistical
Software} 107 (4): 1--32. \url{https://doi.org/10.18637/jss.v107.i04}.

\bibitem[\citeproctext]{ref-chagas2024pretty}
Chagas, Ronan Arraes Jardim, Ben Baumgold, Glen Hertz, Hendrik Ranocha,
Mark Wells, Nathan Boyer, Nicholas Ritchie, et al. 2024.
{``Ronisbr/PrettyTables.jl: V2.4.0.''} Zenodo.
\url{https://doi.org/10.5281/zenodo.13835553}.

\bibitem[\citeproctext]{ref-PlotsJL}
Christ, Simon, Daniel Schwabeneder, Christopher Rackauckas, Michael
Krabbe Borregaard, and Thomas Breloff. 2023. {``Plots.jl -- a User
Extendable Plotting API for the Julia Programming Language.''}
https://doi.org/\url{https://doi.org/10.5334/jors.431}.

\bibitem[\citeproctext]{ref-danisch2021makie}
Danisch, Simon, and Julius Krumbiegel. 2021. {``{Makie.jl}: Flexible
High-Performance Data Visualization for {Julia}.''} \emph{Journal of
Open Source Software} 6 (65): 3349.
\url{https://doi.org/10.21105/joss.03349}.

@@

\bibitem[\citeproctext]{ref-innes2018fashionable}
Innes, Michael, Elliot Saba, Keno Fischer, Dhairya Gandhi, Marco
Concetto Rudilosso, Neethu Mariya Joy, Tejan Karmali, Avik Pal, and
Viral Shah. 2018. {``Fashionable Modelling with Flux.''}
\url{https://arxiv.org/abs/1811.01457}.

\bibitem[\citeproctext]{ref-innes2018flux}
Innes, Mike. 2018. {``Flux: {Elegant} Machine Learning with {Julia}.''}
\emph{Journal of Open Source Software} 3 (25): 602.
\url{https://doi.org/10.21105/joss.00602}.

@@

\begin{tcolorbox}[enhanced jigsaw, rightrule=.15mm, toprule=.15mm, opacitybacktitle=0.6, colback=white, breakable, coltitle=black, colframe=quarto-callout-warning-color-frame, bottomtitle=1mm, toptitle=1mm, titlerule=0mm, leftrule=.75mm, left=2mm, colbacktitle=quarto-callout-warning-color!10!white, arc=.35mm, title=\textcolor{quarto-callout-warning-color}{\faExclamationTriangle}\hspace{0.5em}{Warning}, opacityback=0, bottomrule=.15mm]

@@

\subsection{Training Details}\label{sec-app-training}

In this section, we describe the training procedure in detail. While the
details laid out here are not crucial for understanding our proposed
approach, they are of importance to anyone looking to implement
counterfactual training.

@@

\begin{tcolorbox}[enhanced jigsaw, rightrule=.15mm, toprule=.15mm, opacitybacktitle=0.6, colback=white, breakable, coltitle=black, colframe=quarto-callout-note-color-frame, bottomtitle=1mm, toptitle=1mm, titlerule=0mm, leftrule=.75mm, left=2mm, colbacktitle=quarto-callout-note-color!10!white, arc=.35mm, title=\textcolor{quarto-callout-note-color}{\faInfo}\hspace{0.5em}{Note}, opacityback=0, bottomrule=.15mm]

@@

For the initial round of experiments we employed a different training
objective and procedure that led to promising results for some
hyperparameter choices, but suffered from training instabilities.

@@

  \begin{itemize}
  \tightlist
  \item
    Decisiono. Threshold: \texttt{0.75,\ 0.9,\ 0.95}
  \item
    \(\lambda_{\text{cost}}\): \texttt{0.0,\ 0.1}
  \item
    \(\lambda_{\text{div}}\): \texttt{0.1,\ 0.5,\ 1.0,\ 10.0}
  \item
    Maximum Iterations: \texttt{5,\ 25,\ 50}
  \item
    Optimizerimizer: \texttt{sgd}
  \end{itemize}
\item
  Generator: \texttt{ecco,\ generic,\ revise}
\item
  Training Parameters:

@@

  \toprule
  \textbf{Objective} & \textbf{$\lambda_{\text{div}} (\text{train})$} & \textbf{Generator} & \textbf{Value} & \textbf{Std} \\\midrule
  \endfirsthead
  \toprule
  \textbf{Objective} & \textbf{$\lambda_{\text{div}} (\text{train})$} & \textbf{Generator} & \textbf{Value} & \textbf{Std} \\\midrule
  \endhead
  \bottomrule
  \multicolumn{5}{r}{Continuing table below.}\\
  \bottomrule
  \endfoot
  \endlastfoot
  full & 0.01 & \textit{ECCo} & $-9.91 \cdot 10^{11}$ & $2.25 \cdot 10^{12}$ \\
  full & 0.01 & \textit{Generic} & $-5.71 \cdot 10^{17}$ & $1.3 \cdot 10^{18}$ \\
  \color{blue}{\textbf{full}} & \color{blue}{\textbf{0.01}} & \color{blue}{\textbf{REVISE}} & \color{blue}{\textbf{-15.6}} & \color{blue}{\textbf{13.2}} \\
  vanilla & 0.01 & \textit{ECCo} & -4.28 & 3.52 \\
  vanilla & 0.01 & \textit{Generic} & -4.45 & 3.47 \\
  vanilla & 0.01 & \textit{REVISE} & -4.91 & 4.24 \\
  full & 0.05 & \textit{ECCo} & $-5.63 \cdot 10^{5}$ & $1.28 \cdot 10^{6}$ \\
  full & 0.05 & \textit{Generic} & $-8.35 \cdot 10^{17}$ & $1.9 \cdot 10^{18}$ \\
  full & 0.05 & \textit{REVISE} & -15 & 12.6 \\
  vanilla & 0.05 & \textit{ECCo} & -4.4 & 3.66 \\
  \color{blue}{\textbf{vanilla}} & \color{blue}{\textbf{0.05}} & \color{blue}{\textbf{Generic}} & \color{blue}{\textbf{-4.38}} & \color{blue}{\textbf{3.48}} \\
  vanilla & 0.05 & \textit{REVISE} & -4.94 & 4.22 \\
  full & 0.1 & \textit{ECCo} & $-6.74 \cdot 10^{5}$ & $1.53 \cdot 10^{6}$ \\
  full & 0.1 & \textit{Generic} & $-1.71 \cdot 10^{11}$ & $3.9 \cdot 10^{11}$ \\
  full & 0.1 & \textit{REVISE} & -15.6 & 13.2 \\
  vanilla & 0.1 & \textit{ECCo} & -4.28 & 3.52 \\
  vanilla & 0.1 & \textit{Generic} & -4.45 & 3.48 \\
  vanilla & 0.1 & \textit{REVISE} & -4.91 & 4.25 \\
  \color{blue}{\textbf{full}} & \color{blue}{\textbf{0.5}} & \color{blue}{\textbf{ECCo}} & \color{blue}{\textbf{-11.8}} & \color{blue}{\textbf{9.83}} \\
  full & 0.5 & \textit{Generic} & $-1.06 \cdot 10^{18}$ & $2.42 \cdot 10^{18}$ \\
  full & 0.5 & \textit{REVISE} & -15 & 12.6 \\
  vanilla & 0.5 & \textit{ECCo} & -4.4 & 3.65 \\
  vanilla & 0.5 & \textit{Generic} & -4.38 & 3.48 \\
  vanilla & 0.5 & \textit{REVISE} & -4.95 & 4.22 \\
  full & 1 & \textit{ECCo} & -11.5 & 11.1 \\
  full & 1 & \textit{Generic} & $-1.71 \cdot 10^{11}$ & $3.88 \cdot 10^{11}$ \\
  \color{blue}{\textbf{full}} & \color{blue}{\textbf{1}} & \color{blue}{\textbf{REVISE}} & \color{blue}{\textbf{-15.7}} & \color{blue}{\textbf{13.3}} \\
  vanilla & 1 & \textit{ECCo} & -4.28 & 3.51 \\
  vanilla & 1 & \textit{Generic} & -4.44 & 3.47 \\
  vanilla & 1 & \textit{REVISE} & -4.91 & 4.25 \\
  full & 5 & \textit{ECCo} & -3.99 & 3.12 \\
  full & 5 & \textit{Generic} & $-4.88 \cdot 10^{17}$ & $1.11 \cdot 10^{18}$ \\
  full & 5 & \textit{REVISE} & -14.6 & 12.1 \\
  vanilla & 5 & \textit{ECCo} & -4.4 & 3.65 \\
  \color{blue}{\textbf{vanilla}} & \color{blue}{\textbf{5}} & \color{blue}{\textbf{Generic}} & \color{blue}{\textbf{-4.38}} & \color{blue}{\textbf{3.48}} \\
  vanilla & 5 & \textit{REVISE} & -4.95 & 4.22 \\
  full & 10 & \textit{ECCo} & -2.31 & 0.735 \\
  full & 10 & \textit{Generic} & $-1.7 \cdot 10^{11}$ & $3.86 \cdot 10^{11}$ \\
  full & 10 & \textit{REVISE} & -15.5 & 13 \\
  vanilla & 10 & \textit{ECCo} & -4.28 & 3.51 \\
  vanilla & 10 & \textit{Generic} & -4.44 & 3.47 \\
  vanilla & 10 & \textit{REVISE} & -4.91 & 4.24 \\
  \color{blue}{\textbf{full}} & \color{blue}{\textbf{15}} & \color{blue}{\textbf{ECCo}} & \color{blue}{\textbf{-2.01}} & \color{blue}{\textbf{0.488}} \\
  full & 15 & \textit{Generic} & $-4.91 \cdot 10^{17}$ & $1.12 \cdot 10^{18}$ \\
  full & 15 & \textit{REVISE} & -14.4 & 11.7 \\
  vanilla & 15 & \textit{ECCo} & -4.4 & 3.65 \\
  vanilla & 15 & \textit{Generic} & -4.38 & 3.48 \\
  vanilla & 15 & \textit{REVISE} & -4.95 & 4.23 \\\bottomrule

@@

  \toprule
  \textbf{Objective} & \textbf{$\lambda_{\text{cost}} (\text{train})$} & \textbf{Generator} & \textbf{Value} & \textbf{Std} \\\midrule
  \endfirsthead
  \toprule
  \textbf{Objective} & \textbf{$\lambda_{\text{cost}} (\text{train})$} & \textbf{Generator} & \textbf{Value} & \textbf{Std} \\\midrule
  \endhead
  \bottomrule
  \multicolumn{5}{r}{Continuing table below.}\\
  \bottomrule
  \endfoot
  \endlastfoot
  full & 0 & \textit{ECCo} & $-5.32 \cdot 10^{3}$ & $1.21 \cdot 10^{4}$ \\
  full & 0 & \textit{Generic} & $-1.03 \cdot 10^{18}$ & $2.34 \cdot 10^{18}$ \\
  \color{blue}{\textbf{full}} & \color{blue}{\textbf{0}} & \color{blue}{\textbf{REVISE}} & \color{blue}{\textbf{-15.4}} & \color{blue}{\textbf{12.9}} \\
  vanilla & 0 & \textit{ECCo} & -4.34 & 3.58 \\
  vanilla & 0 & \textit{Generic} & -4.41 & 3.48 \\
  vanilla & 0 & \textit{REVISE} & -4.93 & 4.23 \\
  full & 0.001 & \textit{ECCo} & -362 & 811 \\
  full & 0.001 & \textit{Generic} & $-2.65 \cdot 10^{17}$ & $6.04 \cdot 10^{17}$ \\
  full & 0.001 & \textit{REVISE} & -15.5 & 13 \\
  vanilla & 0.001 & \textit{ECCo} & -4.34 & 3.58 \\
  \color{blue}{\textbf{vanilla}} & \color{blue}{\textbf{0.001}} & \color{blue}{\textbf{Generic}} & \color{blue}{\textbf{-4.41}} & \color{blue}{\textbf{3.48}} \\
  vanilla & 0.001 & \textit{REVISE} & -4.93 & 4.23 \\
  full & 0.1 & \textit{ECCo} & $-3.72 \cdot 10^{11}$ & $8.46 \cdot 10^{11}$ \\
  full & 0.1 & \textit{Generic} & $-4.48 \cdot 10^{14}$ & $1.02 \cdot 10^{15}$ \\
  full & 0.1 & \textit{REVISE} & -14.6 & 12.2 \\
  vanilla & 0.1 & \textit{ECCo} & -4.34 & 3.58 \\
  vanilla & 0.1 & \textit{Generic} & -4.41 & 3.48 \\
  vanilla & 0.1 & \textit{REVISE} & -4.93 & 4.24 \\\bottomrule

@@

\section{Computation Details}\label{computation-details}

\subsection{Hardware}\label{hardware}

We performed our experiments on a high-performance cluster. Details
about the cluster will be disclosed upon publication to avoid revealing
information that might interfere with the double-blind review process.
Since our experiments have largely involved highly parallel tasks and
small models, we have made extensive use of multi-processing.

\subsection{Software}\label{software}

All computations were performed in the Julia Programming Language
(\citeproc{ref-bezanson2017julia}{Bezanson et al. 2017}). We have
developed a package for counterfactual training that leverages and
extends the functionality provided by several existing packages, most
notably
\href{https://github.com/JuliaTrustworthyAI/CounterfactualExplanations.jl}{CounterfactualExplanations.jl}
(\citeproc{ref-altmeyer2023explaining}{Altmeyer, Deursen, et al. 2023})
and the \href{https://fluxml.ai/Flux.jl/v0.16/}{Flux.jl} library for
deep learning (\citeproc{ref-innes2018fashionable}{Michael Innes et al.
2018}; \citeproc{ref-innes2018flux}{Mike Innes 2018}). For
data-wrangling and presentation-ready tables we relied on
\href{https://dataframes.juliadata.org/v1.7/}{DataFrames.jl}
(\citeproc{ref-milan2023dataframes}{Bouchet-Valat and Kamiński 2023})
and
\href{https://ronisbr.github.io/PrettyTables.jl/v2.4/}{PrettyTables.jl}
(\citeproc{ref-chagas2024pretty}{Chagas et al. 2024}), respectively. For
plots and visualizations we used both
\href{https://docs.juliaplots.org/v1.40/}{Plots.jl}
(\citeproc{ref-PlotsJL}{Christ et al. 2023}) and
\href{https://docs.makie.org/v0.22/}{Makie.jl}
(\citeproc{ref-danisch2021makie}{Danisch and Krumbiegel 2021}), in
particular \href{https://aog.makie.org/v0.9.3/}{AlgebraOfGraphics.jl}.

### 2025-02-24 paper/sections/appendix.qmd
added Aleks as author to preprint

@@

# Compute {.appendix}

<!-- [@DHPC2022] -->

@@

>>>>

{{< include /paper/sections/other/training.qmd >}}

@@

# Computation Details {.appendix}

<!-- [@DHPC2022] -->
## Hardware

@@

## Software

All computations were performed in the Julia Programming Language [@bezanson2017julia]. We have developed a package for counterfactual training that leverages and extends the functionality provided by several existing packages, most notably [CounterfactualExplanations.jl](https://github.com/JuliaTrustworthyAI/CounterfactualExplanations.jl) [@altmeyer2023explaining] and the [Flux.jl](https://fluxml.ai/Flux.jl/v0.16/) library for deep learning [@innes2018fashionable;@innes2018flux]. For data-wrangling and presentation-ready tables we relied on [DataFrames.jl](https://dataframes.juliadata.org/v1.7/) [@milan2023dataframes] and [PrettyTables.jl](https://ronisbr.github.io/PrettyTables.jl/v2.4/) [@chagas2024pretty], respectively. For plots and visualizations we used both [Plots.jl](https://docs.juliaplots.org/v1.40/) [@PlotsJL] and [Makie.jl](https://docs.makie.org/v0.22/) [@danisch2021makie], in particular [AlgebraOfGraphics.jl](https://aog.makie.org/v0.9.3/).
